---
title: "Senior_Honors_Thesis_Code"
author: "Dayna De La Cruz"
date: "12/24/2020"
output: html_document
---
Still have the three duplicates: RO114, RO139 , RO293
## Loading Packages
```{r, include=TRUE, message=FALSE, warning=FALSE, results="hide"}
#loading needed packages
library(tidyverse)
library(dplyr)
library(readr)
library(cowplot)
library(ggplot2)
library(nnet)
library(ggpubr)
```

## Preparing Data
```{r, include=TRUE, message=FALSE, warning=FALSE, results="hide"}
#Loading and preparing data
Light_Data <- read_csv("~/Desktop/Senior_Honors_Thesis/R_code/Data/Light_Data.csv")
BiomassAlloc_Data <- read_csv("~/Desktop/Senior_Honors_Thesis/R_Code/Data/BiomassAlloc_Data.csv")
Leaf_Damage_Data <- read_csv("~/Desktop/Senior_Honors_Thesis/R_Code/Data/Leaf_Damage_Data.csv")
BiomassAlloc_Data$Tree_ID <- as.factor(BiomassAlloc_Data$Tree_ID)
BiomassAlloc_Data$Seedling_ID <- as.factor(BiomassAlloc_Data$Seedling_ID)
Light_Data$Tree_ID <- as.factor(Light_Data$Tree_ID)
Leaf_Damage_Data <- filter(Leaf_Damage_Data, Sept_survival == "A")

# Wrangling: Merged BiomassAlloc_Data and Leaf_Damage_Data + select/filter needed material 
Biomass_LeafDam<-merge(BiomassAlloc_Data, Leaf_Damage_Data)%>%
  filter(Sept_survival == "A")#filtered for seedlings that were alive by the end of the experiment 

# Wrangling: Merged Biomass_LeafDam and Light_Data
Biomass_Leaf_Light<-merge(Biomass_LeafDam,Light_Data)

#for BiomassAlloc_Data can recreate by merging biomassAlloc with Leaf_Damage_Data, then do filter(Sept_survival == "A")
```

## Leaf Damage vs. Conspecificity
Graph: yes use this one
Results: Seedling with differing conspecificity within the first and fourth leaf damage category did have a significant difference.
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Wrangling needed material
red_oak_LD <- Leaf_Damage_Data %>%
  filter(Seedling_Species == "Red_Oak", Sept_survival == "A") %>%
  group_by(Tree_ID, C_H) %>%
  summarise(LD1 = sum(LD_category_Sept == "1")/n(),
            LD2 = sum(LD_category_Sept == "2")/n(),
            LD3 = sum(LD_category_Sept == "3")/n(),
            LD4 = sum(LD_category_Sept == "4")/n()) %>%
  gather(key = LD_cat, value = LD_proportion, LD1:LD4) %>%
  group_by(C_H, LD_cat) %>%
  summarise(mean_prop_LD = mean(LD_proportion)*100,
            sterr_LD = sd(LD_proportion)/sqrt(length(LD_proportion))*100)


#Bar graph: Leaf damage category vs mean lead damamge across conspecificity
ggplot(aes(x=LD_cat, y= mean_prop_LD, fill = C_H), data=red_oak_LD) +
  geom_bar(stat= "identity", width = .5, position = "dodge") +
  geom_errorbar(aes(ymin = mean_prop_LD - sterr_LD, ymax = mean_prop_LD + sterr_LD), width = .5, position = "dodge") +
  labs(y = "Percent of red oak seedlings (%)",
       x = "Leaf damage category") +
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%")) +
  #scale_fill_discrete(labels = c("Conspecific","Heterospecific"), name = "") +
  theme_classic()+
  theme(legend.position = c(0.6,0.8))+
  scale_fill_manual(values=c('red','lightgray'))+
  guides(fill=guide_legend(title="Conspecificity"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))
```
Two-sampled T-test
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
##Two-sampled T-test
#Filter to each leaf damage category
LD_Cons<- Leaf_Damage_Data %>%
  filter(Seedling_Species == "Red_Oak", Sept_survival == "A", C_H == "C") %>%
  group_by(Tree_ID) %>%
  summarise(LD1C = sum(LD_category_Sept == "1")/n(),
            LD2C = sum(LD_category_Sept == "2")/n(),
            LD3C = sum(LD_category_Sept == "3")/n(),
            LD4C = sum(LD_category_Sept == "4")/n())
LD_Het<- Leaf_Damage_Data %>%
  filter(Seedling_Species == "Red_Oak", Sept_survival == "A", C_H == "H") %>%
  group_by(Tree_ID) %>%
  summarise(LD1H = sum(LD_category_Sept == "1")/n(),
            LD2H = sum(LD_category_Sept == "2")/n(),
            LD3H = sum(LD_category_Sept == "3")/n(),
            LD4H = sum(LD_category_Sept == "4")/n())
tt_LD1 <- t.test(LD_Cons$LD1C, LD_Het$LD1H, alternative = "two.sided", var.equal = FALSE)
tt_LD1
tt_LD2 <- t.test(LD_Cons$LD2C, LD_Het$LD2H, alternative = "two.sided", var.equal = FALSE)
tt_LD2
tt_LD3 <- t.test(LD_Cons$LD3C, LD_Het$LD3H, alternative = "two.sided", var.equal = FALSE)
tt_LD3
tt_LD4 <- t.test(LD_Cons$LD4C, LD_Het$LD4H, alternative = "two.sided", var.equal = FALSE)
tt_LD4 
```


## Leaf Damage vs. Canopy Light  
Kept all the logs only.
Best Graph to present: first boxplot and scatter plot? Scatter plot just to show same pattern of the previous leaf damage bar graph. Are theretoo many variables if we include conspecificity here (second graph) I already added a seperate graph above of conspecificity. 
Second graph is answering following question: Does conspecificity affect the way light affects seedlings within each leaf damage category? Does the way light affect seedlings in each leaf damamge cateogry vary on their conspecificty? Also showing the light distribution.
Results: It seems like there was no significant relationship between light and leaf damage. Is there any way to include conspecificity in the test? Because if so, it would be nice to say: yes consp had an affect on leaf damage, no light did not have an affect in leaf damage but did conspecificity affect the way light affects seedlings within each leaf damage category? 

```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Wrangling: Merged Light_Data and Leaf_Damage_Data + selected/grouped by needed material  
Light_LeafDamage<-merge(Light_Data,Leaf_Damage_Data)%>%
  filter(Sept_survival == "A")%>%
  group_by(C_H)
Light_LeafDamage$LD_category_Sept<- as.factor(Light_LeafDamage$LD_category_Sept)

# Box Plot: Gap Fraction vs. leaf damage
ggplot(Light_LeafDamage, aes(x=LD_category_Sept, y=Gap_Fraction)) + 
  geom_boxplot()+
  labs(x="Leaf Damage Category", y = "Gap Fraction")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  guides(fill=guide_legend(title="Conspecificity"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()

##Box Plot: Gap Fraction vs leaf damage split between C_H (probly not using this)
ggplot(Light_LeafDamage, aes(x=LD_category_Sept, y=Gap_Fraction, fill=C_H)) + 
  geom_boxplot()+
  labs(x="Leaf Damage Category", y = "Gap Fraction")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  guides(fill=guide_legend(title="Conspecificity"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()

##Scatter Plot: Gap Fraction vs leaf damage split between C_H
ggplot(Light_LeafDamage, aes(x=Gap_Fraction, y=LD_category_Sept, color=C_H)) + 
  geom_jitter(width = 0.25, height = 0.25)+
  labs(x="Gap Fraction", y = "Leaf Damage Category")+
  scale_y_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  guides(fill=guide_legend(title="Conspecificity"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
Multinomial Logistical Regression
we are using this because the leaf damamge is connected and not unrelateed categories correct?
need refresher on how to read this, conspecificty was not included in this analysis correct? 
```{r}
# Performing multinomial logistic regression
#Light_LeafDamage$LD_category_Sept2 <- relevel(Light_LeafDamage$LD_category_Sept, ref = "4")
test <- multinom(LD_category_Sept ~ log(Gap_Fraction) , data = Light_LeafDamage)
summary(test)

z <- summary(test)$coefficients/summary(test)$standard.errors
z

## 2-tailed z test
p <- (1 - pnorm(abs(z), 0, 1)) * 2
p
```

## Leaf Damage vs. Evenness (new one added)
Graph: yes use this one
Results: Seedling with differing evenness within each leaf damage category did not have a significant difference. Think about the mean even if it is not significant. ("higher mean")
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Wrangling needed material
red_oak_LD_Eve <- Leaf_Damage_Data %>%
  filter(Seedling_Species == "Red_Oak", Sept_survival == "A") %>%
  group_by(Tree_ID, Plot_Type) %>%
  summarise(LD1 = sum(LD_category_Sept == "1")/n(),
            LD2 = sum(LD_category_Sept == "2")/n(),
            LD3 = sum(LD_category_Sept == "3")/n(),
            LD4 = sum(LD_category_Sept == "4")/n()) %>%
  gather(key = LD_cat, value = LD_proportion, LD1:LD4) %>%
  group_by(Plot_Type, LD_cat) %>%
  summarise(mean_prop_LD = mean(LD_proportion)*100,
            sterr_LD = sd(LD_proportion)/sqrt(length(LD_proportion))*100)


#Bar graph: Leaf damage category vs mean lead damamge across conspecificity
ggplot(aes(x=LD_cat, y= mean_prop_LD, fill = Plot_Type), data=red_oak_LD_Eve) +
  geom_bar(stat= "identity", width = .5, position = "dodge") +
  geom_errorbar(aes(ymin = mean_prop_LD - sterr_LD, ymax = mean_prop_LD + sterr_LD), width = .5, position = "dodge") +
  labs(y = "Percent of red oak seedlings (%)",
       x = "Leaf damage category") +
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%")) +
  theme_classic()+
  theme(legend.position = c(0.6,0.8))+
  scale_fill_manual(values=c('blue','lightgray'))+
  guides(fill=guide_legend(title="Evenness"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))
```
Two-sampled T-test
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
##Two-sampled T-test
#Filter to each leaf damage category
LD_Even<- Leaf_Damage_Data %>%
  filter(Seedling_Species == "Red_Oak", Sept_survival == "A", Plot_Type == "Even") %>%
  group_by(Tree_ID) %>%
  summarise(LD1E = sum(LD_category_Sept == "1")/n(),
            LD2E = sum(LD_category_Sept == "2")/n(),
            LD3E = sum(LD_category_Sept == "3")/n(),
            LD4E = sum(LD_category_Sept == "4")/n())
LD_Uneven<- Leaf_Damage_Data %>%
  filter(Seedling_Species == "Red_Oak", Sept_survival == "A", Plot_Type == "Uneven") %>%
  group_by(Tree_ID) %>%
  summarise(LD1U = sum(LD_category_Sept == "1")/n(),
            LD2U = sum(LD_category_Sept == "2")/n(),
            LD3U = sum(LD_category_Sept == "3")/n(),
            LD4U = sum(LD_category_Sept == "4")/n())
tt_LDE1 <- t.test(LD_Even$LD1E, LD_Uneven$LD1U, alternative = "two.sided", var.equal = FALSE)
tt_LDE1
tt_LDE2 <- t.test(LD_Even$LD2E, LD_Uneven$LD2U, alternative = "two.sided", var.equal = FALSE)
tt_LDE2
tt_LDE3 <- t.test(LD_Even$LD3E, LD_Uneven$LD3U, alternative = "two.sided", var.equal = FALSE)
tt_LDE3
tt_LDE4 <- t.test(LD_Even$LD4E, LD_Uneven$LD4U, alternative = "two.sided", var.equal = FALSE)
tt_LDE4 
```


## Growth Allocation vs. Leaf Damage
### A:B Ratio vs. Leaf Damage
Best Graph to Present: no color
Results: The A:B ratios within each leaf damage category were significantly different. (some of the groups were different from the overall mean). Do I perform Tukey Test? yes, in order to see which box plots are different. Howevever, there was no significant difference between the A:B ratios of each conspecificity within each leaf damage category right???? 
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Scatter Plot + Box Plot: log(A:B ratio) vs leaf damage category
#no color
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=log(A_B_ratio))) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "log(A:B Ratio)")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()

#color C_H
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=log(A_B_ratio), color=C_H)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "log(A:B Ratio)")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
What does the astriks beside the intercept mean again? Looking at the interaction betwen CH and leaf damage and how that affects A:B ratio
ANOVA: Analysis of Variance: for log(A:B Ratio) vs. Leaf Damage
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_A_B<-lm(log(A_B_ratio)~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_A_B)
```
### A:B Ratio Average vs. Leaf Damage
Do i need this?? I think I can scrap

### Aboveground Biomass vs. Leaf Damage & Belowground Biomass vs. Leaf Damage
Results:no sig diff
Best Graphs to Present: Do i really need both graphs? I feel like i def need the no color one for both aboveground and belowground biomass. But shouldnt i have a box plot with onylc cons and no leaf damage seperately? (further below)

#### Aboveground Biomass vs. Leaf Damage
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# log(Aboveground biomass)
Biomass_LeafDam$total_biomass<-(Biomass_LeafDam$Aboveground_biomas_g+Biomass_LeafDam$Belowground_biomas_g)
Biomass_LeafDam$aboveground_fraction<-(Biomass_LeafDam$Aboveground_biomas_g/Biomass_LeafDam$total_biomass)
Biomass_LeafDam$belowground_fraction<-(Biomass_LeafDam$Belowground_biomas_g/Biomass_LeafDam$total_biomass)
# Scatter Plot + Box Plot: log(Aboveground Biomass) vs. Leaf Damage
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=log(Aboveground_biomas_g))) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "log(Aboveground Biomass)")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
#box plot w/ conspecificity
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=log(Aboveground_biomas_g),color=C_H)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "log(Aboveground Biomass)")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()

```
Intercept Significance?
ANOVA: Analysis of Variance: Aboveground Biomass
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_A<-lm(log(Aboveground_biomas_g)~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_A)
```

#### Belowground Biomass vs. Leaf Damage
Graphs: def non color. Do i really need color?
Results: no sig dif
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Scatter Plot + Box Plot: Belowground Biomass vs. Leaf Damage
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=Belowground_biomas_g)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "Belowground Biomass")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
#box plot w/ conspecificity
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=Belowground_biomas_g,color=C_H)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "Belowground Biomass")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance: Belowground Biomass
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_B<-lm(Belowground_biomas_g~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_B)
```

### Aboveground Fractions vs. Leaf Damage & Belowground Fractions vs. Leaf Damage
#### Aboveground Fractions vs. Leaf Damage 
Results: the aboveground biomass fraction results from each leaf damage category were significanly different. Do I perform a Tukey test?? Yes. 

```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Scatter Plot + Box Plot: Aboveground Fraction (aboveground/total biomass)
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=aboveground_fraction)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "Aboveground Biomass Fraction")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance for Aboveground Biomass Fraction
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_AF<-lm(aboveground_fraction~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_AF)
#What if I get the average abovegound fraction for each leaf damage category and then plot as a lm model??
```

#### Belowground Fractions vs. Leaf Damage 
Results: The Belowground Biomass Fraction measurments were significantly different. Tukey test

```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Scatter Plot + Box Plot: Belowground Fraction
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=belowground_fraction)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "Belowground Biomass Fraction")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance for Belowground Biomass Fraction
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_BF<-lm(belowground_fraction~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_BF)
```
#### Leaf Biomass Fraction vs. Leaf Damage (new one)
Note:Shows Small fraction of biomass is allocated ot leaves. Note: thinking about * and + for test
Results: significant!!! Tukey!
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Wrangling Data: creating new column for leaf biomass
Biomass_LeafDam$LeafBiomass_fraction<-(Biomass_LeafDam$`Leaf_biomass _g`/Biomass_LeafDam$total_biomass)
# Wrangling Data: removing na's
Biomass_LeafDam$LeafBiomass_fraction <- na.omit(Biomass_LeafDam$LeafBiomass_fraction)

# Scatter Plot + Box Plot: Leaf Biomass Fraction
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=LeafBiomass_fraction)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "Leaf Biomass Fraction")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance for Leaf Biomass Fraction
Do i need to include the C_H here even if not testing for it? Is it because of Covariates??
The log for the anova was not working due to infinate, NA's. 
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_LB<-lm(LeafBiomass_fraction~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_LB)
```


#### Stem Biomass Fraction vs. vs. Leaf Damage (new one)
Results: Not sig
Note: thinking about * and + for test
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Wrangling Data: creating new column for stem biomass
Biomass_LeafDam$StemBiomass_fraction<-(Biomass_LeafDam$`Stem_biomass _g`/Biomass_LeafDam$total_biomass)

# Scatter Plot + Box Plot: Stem Biomass Fraction
ggplot(Biomass_LeafDam, aes(x=as.factor(LD_category_Sept), y=StemBiomass_fraction)) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Leaf Damage Category", y = "Stem Biomass Fraction")+
  scale_x_discrete(labels = c("0-25%","26-50%","51-75%","76-100%"))+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance for Leaf Biomass Fraction
The log for the anova was not working due to infinate, NA's. Does the log have to be included
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_LD_SB<-lm(StemBiomass_fraction~LD_category_Sept*C_H, data=Biomass_LeafDam)
summary(ANOVA_LD_SB)
```

## A:B Ratio vs. Conspecificity (new one added to seperate)
should i have this one? Is this a good way to express it??
note: past graph sort of testing this.....can use this to develop
box plot: log(A:B ratio vs conspecificity)
Results: There was no significant difference between the seedlings' A:B ratios with differing conspecificities
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Box Plot + Scatter Plot: log(A:B Ratio) vs. Conspecificity 
ggplot(Biomass_LeafDam, aes(x=as.factor(C_H), y=log(A_B_ratio))) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Conspecificity", y = "log(A:B Ratio)")+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance for log(A:B Ratio) vs. Conspecificity
Two samples T-test
Should I just do a two sampled t-test? If I do, i need to check variance first. But do I need to get the avarages of each in a specific format.. did it, need help because not working
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
 #Creating seperate datasets to calculate average A:B ratio for each conspecificity
#Cons <- Biomass_LeafDam %>%
        #select(A_B_ratio,C_H) %>%
        #filter(C_H == "C")%>%
  #summarise(AB_Avg_C = mean(A_B_ratio))

#Het <- Biomass_LeafDam %>%
        #select(A_B_ratio,C_H) %>%
        #filter(C_H == "H")%>%
  #summarise(AB_Avg_H = mean(A_B_ratio))
#AB_Cons <- merge(Cons, Het) # Merging both data sets

# Two sampled T-test: 
#Cons <- Biomass_LeafDam %>%
       # select(A_B_ratio,C_H) %>%
       # filter(C_H == "C")
#var(Cons$A_B_ratio)

#Het <- Biomass_LeafDam %>%
    #    select(A_B_ratio,C_H) %>%
     #   filter(C_H == "H")
#var(Het$A_B_ratio)
#tt_AB_Cons <- t.test(AB_Cons$AB_Avg_C,AB_Cons$AB_Avg_H,var.equal = F)

#ANOVA: Analysis of Variance
ANOVA_AB_Cons<-lm(log(A_B_ratio)~C_H, data=Biomass_LeafDam)
summary(ANOVA_AB_Cons)
```

Stopped here with Jackie
## A:B Ratio vs. Light
### A:B Ratio across light: each seedling

Best graph to present: Keep only the log for both seedling and site level graph (Do i need a log?)
Results: There were no significant relationships between the log(A:B) and the gap fraction in both the individual seedling and site level
Note: do these need logs at all? Do I also need to log transform the Gap Fraction? If so, do not forget to also change the linear regression analysis.
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Scatter plot: A:B across continous light 
ggplot(Biomass_Leaf_Light, aes(x=Gap_Fraction, y=A_B_ratio))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(x = "Gap Fraction (%)", y = "A:B Ratio")+
  theme_bw()

# Scatter plot: log(A:B) across continous light 
ggplot(Biomass_Leaf_Light, aes(x=Gap_Fraction, y=log(A_B_ratio)))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(x = "Gap Fraction (%)", y = "log(A:B Ratio)")+
  theme_bw()
```
Linear Regression Analysis:  log (A:B) vs. Gap Fraction
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#Linear regression analysis (not signifant)
LR_Light_AB<-lm(log(A_B_ratio)~(Gap_Fraction), data=Biomass_Leaf_Light)
summary(LR_Light_AB)
```


### A:B Ratio average across light: each plot
Graph: Keep only the log? Which one do i keep? Does it really need a log?
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Average of A:B per site 
# Wrangling: Created new column to calculaet the Average A:B ratio of each site
AB_Avg<-group_by(Biomass_LeafDam, Tree_ID)%>%
  summarise(AB_Average=mean(A_B_ratio, na.rm = T),
            count=n()) #this will ignore the NA's
AB_Avg_Light<-merge(Light_Data,AB_Avg)

# Scatter plot: A:B average per plot across continous light
ggplot(AB_Avg_Light, aes(x=Gap_Fraction, y=AB_Average))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(x = "Gap Fraction (%)", y = "A:B Ratio Average")+
  theme_bw()

# Scatter plot: log(A:B average) per plot across continous light
ggplot(AB_Avg_Light, aes(x=Gap_Fraction, y=log(AB_Average)))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(x = "Gap Fraction (%)", y = "log(A:B Ratio Average)")+
  theme_bw()
```
Linear Regression Analysis: log (A:B Average) vs. Gap Fraction
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#Linear regression analysis (not signifant)
LR_Light_AB_Avg<-lm(log(AB_Average)~Gap_Fraction, data=AB_Avg_Light)
summary(LR_Light_AB_Avg)
```

## Growth Allocation vs. Evenness (new one added)
Results"
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
# Box Plot + Scatter Plot: log(A:B Ratio) vs. Evenness 
ggplot(Biomass_LeafDam, aes(x=as.factor(Plot_Type), y=log(A_B_ratio))) + 
  geom_jitter(width = 0.25, height = 0, alpha=0.5)+
  geom_boxplot(alpha=0.1)+
  labs(x="Evenness", y = "log(A:B Ratio)")+
  theme(axis.title.x = element_text(size=15))+theme(axis.title.y = element_text(size=15))+
  theme_classic()
```
ANOVA: Analysis of Variance for log(A:B Ratio) vs. Evenness
Results: There was no significant difference between the seedlings' A:B ratios with differing evenness
```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#ANOVA: Analysis of Variance
ANOVA_AB_Even<-lm(log(A_B_ratio)~Plot_Type, data=Biomass_LeafDam)
summary(ANOVA_AB_Even)
```